Quasi-consistent efficient meshfree thin shell formulation with naturally stabilized enforced essential boundary conditions

### 2024-04-06 boundary.tex
revised 1

+ (\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} \right ) = - \sum_{I=1}^{n_p}\delta d_I \cdot \boldsymbol f_I

@@

&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  \boldsymbol q^T \boldsymbol d^\alpha_N d\Omega \\
&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \boldsymbol a_\beta(\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  N^{\alpha\beta h} d\Omega \\

@@

where

@@

        \boldsymbol K_{IJ} = \int_\Omega \tilde{\boldsymbol \varepsilon}_{\alpha\beta I} hC^{\alpha\beta\gamma\eta}\tilde{\boldsymbol \varepsilon}_{\gamma\eta J} d\Omega + \int_\Omega \tilde{\boldsymbol \kappa}_{\alpha\beta I} \frac{h^3}{12}C^{\alpha\beta\gamma\eta} \tilde{\boldsymbol \kappa}_{\alpha\beta J} d\Omega

@@

        \tilde{\boldsymbol K}_{IJ} = &- \int_{\Gamma_v} (\Psi_I \tilde{\boldsymbol T}_{NJ} + \tilde{\boldsymbol T}_{NJ} \Psi_J) d\Gamma \\
                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}J} + \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\

@@

                     &+ \underbrace{\sum_{i=1}^3\frac{\alpha_{vi}}{2} \int_{\Gamma_v} \boldsymbol v \cdot \boldsymbol v d\Gamma 

@@

where the consistent term generated from the Lagrangian multiplier method contributes to enforce the essential boundary, and meet the variational consistency condition. However, the consistent term cannot always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term, in which $\alpha_{vi}$'s, $\alpha_\theta$ and $\alpha_C$ are experimental artificial parameters in the penalty method. With a standard variational argument, the corresponding weak form can be stated as:

@@

\sum_{J=1}^{n_p}(\boldsymbol K_{IJ} + \boldsymbol K^c_{IJ} + \boldsymbol K^s_{IJ}) \boldsymbol d_J = \boldsymbol f_I + \boldsymbol f^c + \boldsymbol f^s

@@

where the stiffness $\boldsymbol K_{IJ}$ is identical with Eq. (\ref{de1}). $\boldsymbol K^c_{IJ}$ and $\boldsymbol K^s_{IJ}$ are the stiffness matrices for consistent and stabilized terms, respectively, and have the following form:

@@

\boldsymbol K^c_{IJ} = &- \int_{\Gamma_v} (\Psi_I \boldsymbol T_{NJ} + \boldsymbol T_{NJ} \Psi_J) d\Gamma \\
                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}J} + \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\

>>>>

+ (\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} \right ) = - \sum_{I=1}^{n_p}\delta \boldsymbol d_I \cdot \boldsymbol f_I

@@

&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})  \boldsymbol q^T \boldsymbol d^\alpha_N d\Omega \\
&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \boldsymbol a_\beta(\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})  N^{\alpha\beta h} d\Omega \\

@@

where the components of stiffness matrices and force vectors in discrete equilibrium equations can be evaluated as follows:

@@

        \boldsymbol K_{IJ} = \int_\Omega \tilde{\boldsymbol \varepsilon}_{\alpha\beta I} hC^{\alpha\beta\gamma\eta}\tilde{\boldsymbol \varepsilon}_{\gamma\eta J} d\Omega + \int_\Omega \tilde{\boldsymbol \kappa}_{\alpha\beta I} \frac{h^3}{12}C^{\alpha\beta\gamma\eta} \tilde{\boldsymbol \kappa}_{\gamma\eta J} d\Omega

@@

        \tilde{\boldsymbol K}_{IJ} = &- \int_{\Gamma_v} (\Psi_I \tilde{\boldsymbol T}_{NJ} + \tilde{\boldsymbol T}_{NI} \Psi_J) d\Gamma \\
                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}J} + \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}I} \Psi_{J,\gamma}n^\gamma)d\Gamma \\

@@

                     &+ \underbrace{\sum_{i=1}^3\frac{\alpha_{vi}}{2} \int_{\Gamma_v} (\boldsymbol v \cdot \boldsymbol a_i)^2 d\Gamma 

@@

where the consistent term generated from the Lagrangian multiplier method contributes to enforce the essential boundary, and meet the variational consistency condition. However, the consistent term can not always ensure the coercivity of stiffness, so the penalty method is introduced to serve as a stabilized term, in which $\alpha_{vi}$ is the experimental artificial parameter to enforce the displacement towards the $\boldsymbol a_i$ direction, $\alpha_\theta$ and $\alpha_C$ are parameters to enforce rotation and corner deflection, respectively. With a standard variational argument, the corresponding weak form can be stated as:

@@

(\boldsymbol K + \boldsymbol K^c + \boldsymbol K^s) \boldsymbol d = \boldsymbol f + \boldsymbol f^c + \boldsymbol f^s

@@

where the stiffness $\boldsymbol K$ is identical with Eq. (\ref{de1}). $\boldsymbol K^c$ and $\boldsymbol K^s$ are the stiffness matrices for consistent and stabilized terms, respectively, and their components have the following form:

@@

\boldsymbol K^c_{IJ} = &- \int_{\Gamma_v} (\Psi_I \boldsymbol T_{NJ} + \boldsymbol T_{NI} \Psi_J) d\Gamma \\
                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}J} + \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}I} \Psi_{J,\gamma}n^\gamma)d\Gamma \\

### 2024-04-06 conclusion.tex
revised 1

\section{Conclusion}\label{conclusion}
In this study, an efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions.  Mixed formulation with the Hu-Washizu principle weak form is adopted, where the traditional meshfree shape functions discretized the displacement, and the strains and stresses were expressed by the reproducing kernel smoothed gradients and the covariant smoothed gradients, respectively. The smoothed gradient naturally embedded the first second-order integration constraints and has a quasi variational consistency for the curved models in each integration cell. Owing to the Hu-Washizu variational principle, the essential boundary condition enforcement has a similar form with the conventional Nitsche’s method; both have consistent and stabilized terms. The costly high order derivatives in the Nitsche’s consistent term have been replaced by the smoothed gradients, which improved the computational speed due to the reproducing kernel gradient smoothing framework. Furthermore, the stabilized term naturally existed in the Hu-Washizu weak form, and the artificial parameter needed in Nitsche’s stabilized term has vanished, which can automatically maintain the coercivity for the stiffness matrix. Based on general reproducing kernel gradient smoothing framework, the proposed methodology can be trivially extended to high order basis meshfree formulation. The numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation showed excellent accuracy, efficiency, and stability.

>>>>

\section{Conclusion}\label{conclusion}
In this study, an efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions.  Mixed formulation with the Hu-Washizu principle weak form is adopted, where the traditional meshfree shape functions discretized the displacement, and the strains and stresses were expressed by the reproducing kernel smoothed gradients and the covariant bases, respectively. The smoothed gradient naturally embedded the first second-order integration constraints and has a quasi variational consistency for the curved models in each integration cell. Owing to the Hu-Washizu variational principle, the essential boundary condition enforcement has a similar form with the conventional Nitsche’s method; both have consistent and stabilized terms. The costly high order derivatives in the Nitsche’s consistent term have been replaced by the smoothed gradients, which improved the computational speed due to the reproducing kernel gradient smoothing framework. Furthermore, the stabilized term naturally existed in the Hu-Washizu weak form, and the artificial parameter needed in Nitsche’s stabilized term has vanished, which can automatically maintain the coercivity for the stiffness matrix. Based on general reproducing kernel gradient smoothing framework, the proposed methodology can be trivially extended to high order basis meshfree formulation. The numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation showed excellent accuracy, efficiency, and stability.

### 2024-04-06 frontmatter.tex
revised 1

\begin{frontmatter}
    % \title{A Hu-Washizu variational consistent meshfree thin shell formulation naturally accommodating essential boundary conditions}
    % \title{Quasi-consistent efficient meshfree thin shell formulation to naturally accommodate essential boundary conditions}
    \title{Quasi-consistent efficient meshfree thin shell formulation with penalty-free essential boundary condition enforcement}
    \author[1]{Junchao Wu\corref{cor1}}
    \ead{jcwu@hqu.edu.cn}
    \author[1]{Yangtao Xu}
    \author[1]{Bin Xu}
    \author[1]{Syed Humayun Basha}

@@

\begin{abstract}
This research proposed an eficient and quasi-consistent meshfree thin shell formulation with penalty-free enforcement of essential boundary conditions. Within the framework of the Hu-Washizu variational principle, a mixed formulation of displacements, strains and stresses is employed in this approach, where the displacements are discretized using meshfree shape functions, and the strains and stresses are expressed using smoothed gradients, covariant smoothed gradients and covariant bases. The smoothed gradients satisfy the first second-order integration constraint and have variational consistency for polynomial strains and stresses. Owing to Hu-Washizu variational principle, the essential boundary conditions automatically arise in its weak form. As a result, the suggested technique's enforcement of essential boundary conditions resembles that of the traditional Nitsche's method. Contrary to Nitsche's method, the costly higher order derivatives of conventional meshfree shape functions were replaced by the smoothed gradients with fast computation, which improve the efficiency. Meanwhile, the proposed formulation features a naturally stabilized term without adding any artificial stabilization factors, which eliminates the employment of penalty method as a stabilization. The efficacy of the proposed Hu-Washizu meshfree thin shell formulation is illustrated by a set of classical standard thin shell problems.
\end{abstract}
\begin{keyword}
Meshfree \sep Thin shell \sep Hu-Washizu variational principle \sep Reproducing kernel gradient smoothing \sep Essential boundary condition
\end{keyword}
\end{frontmatter}

>>>>

\begin{frontmatter}
    % \title{A Hu-Washizu variational consistent meshfree thin shell formulation naturally accommodating essential boundary conditions}
    % \title{Quasi-consistent efficient meshfree thin shell formulation to naturally accommodate essential boundary conditions}
    % \title{Quasi-consistent efficient meshfree thin shell formulation with penalty-free essential boundary condition enforcement}
    \title{Quasi-consistent efficient meshfree thin shell formulation with naturally stabilized enforced essential boundary conditions}
    \author[1]{Junchao Wu\corref{cor1}}
    \ead{jcwu@hqu.edu.cn}
    \author[1]{Yangtao Xu}
    \author[1]{Bin Xu}
    \author[1]{Syed Humayun Basha}

@@

\begin{abstract}
This research proposed an efficient and quasi-consistent meshfree thin shell formulation with naturally stabilized enforcement of essential boundary conditions. Within the framework of the Hu-Washizu variational principle, a mixed formulation of displacements, strains and stresses is employed in this approach, where the displacements are discretized using meshfree shape functions, and the strains and stresses are expressed using smoothed gradients and covariant bases. The smoothed gradients satisfy the first second-order integration constraint and observed variational consistency for polynomial strains and stresses. Owing to Hu-Washizu variational principle, the essential boundary conditions automatically arise in its weak form. As a result, the suggested technique's enforcement of essential boundary conditions resembles that of the traditional Nitsche's method. Contrary to Nitsche's method, the costly higher order derivatives of conventional meshfree shape functions are replaced by the smoothed gradients with fast computation, which improve the efficiency. Meanwhile, the proposed formulation features a naturally stabilized term without adding any artificial stabilization factors, which eliminates the application of penalty method as a stabilization. Further, the efficacy of the proposed Hu-Washizu meshfree thin shell formulation is illustrated by a set of classical standard thin shell problems.
\end{abstract}
\begin{keyword}
Meshfree \sep Thin shell \sep Hu-Washizu variational principle \sep Reproducing kernel gradient smoothing \sep Essential boundary condition
\end{keyword}
\end{frontmatter}

### 2024-04-06 kinematics.tex
revised 1

In accordance with the Kirchhoff hypothesis, the thickness of shell will not change, and the deformation related with direction of $\xi^3$ will vanish, i.e. $\epsilon_{3i}=0$. Thus, the rotation $\boldsymbol \theta$ can be rewritten as:
\begin{equation}\label{a3}
\epsilon_{3i} = 0 \Rightarrow
\left \{
\begin{split}
&\boldsymbol \theta \cdot \boldsymbol a_\alpha =- \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \\
&\boldsymbol \theta \cdot \boldsymbol a_3 = 0
\end{split}
\right .
\Rightarrow \boldsymbol \theta = - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \boldsymbol a^\alpha
\end{equation}
where $\boldsymbol a^\alpha$'s is the in-plane contravariant base vector, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function. The detailed derivation of Eq. \ref{a3} can be found in reference \cite{benzaken2021}.

Furthermore, substituting Eq. (\ref{a3}) into Eq. (\ref{kappa1}) leads to:
\begin{equation}
\kappa_{\alpha\beta} = (\Gamma^\gamma_{\alpha\beta} \boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}) \cdot \boldsymbol a_3 = - \boldsymbol v_{,\alpha}\vert_\beta \cdot \boldsymbol a_3
\end{equation}
in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely the Christoffel symbol of the second kind, and $\boldsymbol v_{,\alpha}\vert\beta$ is the in-plane covariant derivative of $\boldsymbol v_{,\alpha}$, i.e. $\boldsymbol v_{,\alpha}\vert_\beta = \Gamma^\gamma_{\alpha\beta}\boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}$.

@@

Moreover, the natural boundary conditions should be applied by Lagrangian multiplier method with displacement $\boldsymbol v$ regarded as multiplier. Thus, then the new complementary energy functional namely $\Pi$ is given by:
\begin{equation} \label{functional}
\begin{split}
&\Pi(\boldsymbol v, \varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta}) \\
=&\Pi_C(\varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta})
+ \int_{\Gamma_M} \theta_{\boldsymbol n} (M_{\boldsymbol{nn}} - \bar M_{\boldsymbol{nn}}) d\Gamma \\
- &\int_{\Gamma_T} \boldsymbol v \cdot (\boldsymbol T - \bar{\boldsymbol T})d\Gamma - \boldsymbol v \cdot \boldsymbol a_3 (P - \bar{P})_{\boldsymbol x \in C_P}
- \int_\Omega \boldsymbol v \cdot (\boldsymbol b - \bar{\boldsymbol b}) d\Omega 
\end{split}
\end{equation}
where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol nn}$ and $\bar P$ are the prescribed traction, bending moment and concentrated force on the edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$, respectively. All the specified boundaries meet the following geometric relationships:
\begin{equation}\label{geo}
\begin{cases}
\Gamma=\Gamma_v \cup \Gamma_T \cup \Gamma_\theta \cup \Gamma_M, \quad C = C_v \cup C_P, \\
\Gamma_v \cap \Gamma_T = \Gamma_\theta \cap \Gamma_M = C_v \cap C_P = \varnothing
\end{cases}
\end{equation}
and $\bar{\boldsymbol b}$ stands for the prescribed body force in $\Omega$, $\boldsymbol b$ can be written based on Euler-Lagrange equations \cite{benzaken2021} as:
\begin{equation}
\boldsymbol b = \boldsymbol b_N + \boldsymbol b_M \rightarrow
\begin{cases}
\boldsymbol b_N = (\boldsymbol a_\alpha N^{\alpha\beta})\vert_\beta \\
\boldsymbol b_M = (\boldsymbol a_3 M^{\alpha\beta})\vert_{\alpha\beta}
\end{cases}
\end{equation}

>>>>

In accordance with the Kirchhoff hypothesis, the thickness of shell will not change, and the deformation related with direction of $\xi^3$ will vanish, i.e. $\epsilon_{3i}=0$. Thus, the rotation $\boldsymbol \theta$ can be rewritten as:
\begin{equation}\label{a3}
\epsilon_{3i} = 0 \Rightarrow
\left \{
\begin{split}
&\boldsymbol \theta \cdot \boldsymbol a_\alpha =- \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \\
&\boldsymbol \theta \cdot \boldsymbol a_3 = 0
\end{split}
\right .
\Rightarrow \boldsymbol \theta = - \boldsymbol v_{,\alpha} \cdot \boldsymbol a_3 \boldsymbol a^\alpha
\end{equation}
where $\boldsymbol a^\alpha$'s is the in-plane contravariant base vector, $\boldsymbol a^\alpha \cdot \boldsymbol a_\beta = \delta^\alpha_\beta$, $\delta$ is the Kronecker delta function. The detailed derivation of Eq. \ref{a3} can be found in \cite{benzaken2021}.

Furthermore, on substituting Eq. (\ref{a3}) into Eq. (\ref{kappa1}) leads to:
\begin{equation}
\kappa_{\alpha\beta} = (\Gamma^\gamma_{\alpha\beta} \boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}) \cdot \boldsymbol a_3 = - \boldsymbol v_{,\alpha}\vert_\beta \cdot \boldsymbol a_3
\end{equation}
in which $\Gamma^\gamma_{\alpha\beta} = \boldsymbol a_{\alpha,\beta} \cdot \boldsymbol a^\gamma$ is namely the Christoffel symbol of the second kind, and $\boldsymbol v_{,\alpha}\vert_\beta$ is the in-plane covariant derivative of $\boldsymbol v_{,\alpha}$, i.e. $\boldsymbol v_{,\alpha}\vert_\beta = \Gamma^\gamma_{\alpha\beta}\boldsymbol v_{,\gamma} - \boldsymbol v_{,\alpha\beta}$.

@@

Moreover, the natural boundary conditions should be applied by Lagrangian multiplier method with displacement $\boldsymbol v$ regarded as multiplier. Thus, then the new complementary energy functional namely $\Pi$ is given by:
\begin{equation} \label{functional}
\begin{split}
&\Pi(\boldsymbol v, \varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta}) \\
=&\Pi_C(\varepsilon_{\alpha\beta},\kappa_{\alpha\beta},N^{\alpha\beta},M^{\alpha\beta})
+ \int_{\Gamma_M} \theta_{\boldsymbol n} (M_{\boldsymbol{nn}} - \bar M_{\boldsymbol{nn}}) d\Gamma \\
- &\int_{\Gamma_T} \boldsymbol v \cdot (\boldsymbol T - \bar{\boldsymbol T})d\Gamma - \boldsymbol v \cdot \boldsymbol a_3 (P - \bar{P})_{\boldsymbol x \in C_P}
- \int_\Omega \boldsymbol v \cdot (\boldsymbol b - \bar{\boldsymbol b}) d\Omega 
\end{split}
\end{equation}
where $\bar{\boldsymbol T}$, $\bar M_{\boldsymbol{nn}}$ and $\bar P$ are the prescribed traction, bending moment and concentrated force on edges $\Gamma_T$, $\Gamma_M$ and corner $C_P$ respectively. All the specified boundaries meet the following geometric relationships:
\begin{equation}\label{geo}
\begin{cases}
\Gamma=\Gamma_v \cup \Gamma_T \cup \Gamma_\theta \cup \Gamma_M, \quad C = C_v \cup C_P, \\
\Gamma_v \cap \Gamma_T = \Gamma_\theta \cap \Gamma_M = C_v \cap C_P = \varnothing
\end{cases}
\end{equation}
and $\bar{\boldsymbol b}$ stands for the prescribed body force in $\Omega$, $\boldsymbol b$ can be written based on Euler-Lagrange equations \cite{benzaken2021} as:
\begin{equation}
\boldsymbol b = \boldsymbol b_N + \boldsymbol b_M \rightarrow
\begin{cases}
\boldsymbol b_N = (\boldsymbol a_\alpha N^{\alpha\beta})\vert_\beta \\
\boldsymbol b_M = (\boldsymbol a_3 M^{\alpha\beta})\vert_{\alpha\beta}
\end{cases}
\end{equation}
